\chapter{Further Strategies}
\section{UNSAT Core}
In \tiny IA\_UNSAT \normalsize rule, the negation of $\mathring\Pi$ is added into the interval constraint so that $\mathring\Pi$ will not be explore again later because it make the constraint unsatisfiable. If we can find $\mathring\Pi'$ such that $\mathring\Pi = \mathring\Pi' \wedge \mathring\Pi''$ and $\varphi$ is $\{\mathring\Pi'^p_{IA}\}$-UNSAT, we can add $\neg\mathring\Pi'$ into interval constraint instead of $\mathring\Pi$ to reduce the search space.

\begin{example}
Consider the constraint $\varphi = x^2 + y^2 < 1$. Suppose in the \tiny IA\_UNSAT \normalsize rule, we have $\Pi = (x \in \langle 2, 3 \rangle \vee x \in \langle 0, 2 \rangle) \wedge (y \in \langle 0, 1 \rangle y \in \langle -1, 0 \rangle)$ and $\mathring\Pi = x \in \langle 2, 3 \rangle \wedge y \in \langle 0, 1 \rangle$. The conditions of \tiny IA\_UNSAT \normalsize are satisfied, $\neg \mathring\Pi$ is added into the interval constraint which becomes $\Pi \wedge \neg \mathring\Pi$. The new interval constraint contains $\{x \in \langle 2, 3 \rangle, y \in \langle -1, 0 \rangle\}$ as one of its solution. However, with $\mathring\Pi' = x \in \langle 2, 3 \rangle$, we have $\varphi$ is $\{\mathring\Pi'^p_{IA}\}$-UNSAT and by adding $\neg\mathring\Pi'$ to the interval constraint, $\{x \in \langle 2, 3 \rangle, y \in \langle -1, 0 \rangle\}$ is also removed from the search space.
\end{example}

The constraint $\varphi = \bigwedge\limits_{j=1}^n f_j > 0$ is $\mathring\Pi$-UNSAT when $f_k > 0$ is $\mathring\Pi$-UNSAT with some $k \in \{1, 2, \cdots, n\}$. We have two ideas for computing UNSAT core.
\begin{enumerate}
\item \emph{UNSAT core 1:} A sub-polynomial $f_k'$ of $f_k$ such that
\begin{itemize}
\item $f_k' > 0$ is $\mathring\Pi$-UNSAT implies that $f_k$ is $\mathring\Pi$-UNSAT, and
\item $f_k'$ is in fact $\mathring\Pi$-UNSAT.
\end{itemize} 
In this case, we just take $\mathring\Pi' = \bigwedge\limits_{v_i \in var(f_k)}v_i \in \langle l_i, h_j \rangle$.
\item \emph{UNSAT core 2:} Check all the possible cases if $\mathring\Pi'$.
\end{enumerate}

\begin{example}
Consider again the constraint $\varphi = x^2 + y^2 < 1$ or $1 - x^2 - y^2 > 0$. In the \tiny IA\_UNSAT \normalsize rule, we also have $\Pi = (x \in \langle 2, 3 \rangle \vee x \in \langle 0, 2 \rangle) \wedge (y \in \langle 0, 1 \rangle y \in \langle -1, 0 \rangle)$ and $\mathring\Pi = x \in \langle 2, 3 \rangle \wedge y \in \langle 0, 1 \rangle$. Here, $\varphi$ is $\Pi$-UNSAT. In addition, $1 - x^2$ is the UNSAT core of $1 - x^2 - y^2$ because 
\begin{itemize}
\item $1 - x^2$ is $\Pi^p_{IA}$-UNSAT implies that $1 - x^2 - y^2$ is $\Pi^p_{IA}$-UNSAT, and 
\item The constraint $1 - x^2 > 0$ is in fact $\Pi^p_{IA}$-UNSAT.
\end{itemize} 
\end{example}

\subsection*{Preliminary Experiments}

\section{Test Case Generation}
\section{Box Decomposition}